Body Area Network Platform Utilizing Energy-Efficient Routing of Physiological Data

### 2011-09-16 docs/thesis/thesis.tex
Changed title, removed page number from title page, added links.

%\addtolength{\oddsidemargin}{0.5in}
%\addtolength{\evensidemargin}{0.5in}
%\addtolength{\topmargin}{0.25in}
%\addtolength{\textwidth}{-0.5in}

\begin{document}
\title{Specialized Cost Function for Maximizing Body Area Network Lifetime Using Global Routing Algorithms\\
Masters Thesis}
\author{Alvaro Prieto\\
BS/MS Electrical Engineering\\
Electrical and Microelectronic Engineering Department\\
Rochester Institute of Technology\\
Rochester, NY\\
\texttt{axp8664@rit.edu}}

\thispagestyle{empty}
\maketitle

@@

\tableofcontents

@@

\listoffigures

@@

Finally, the program produced a graphical output. The graphical output began as a simple experiment to see a visual representation of the network. It was later expanded to generate graphs of the network, and all available connections, as the RSSI data was sampled. Due to the large number of links between all of the nodes, this graphic was not useful. The final implementation, which can be seen in Figure~\ref{fig:networkgraph1}, only displayed the links used in a specific round of routing. The link labels display the transmit power required by each node to meet the specific link. The generated graphs can later be put together to form an animation that shows the network changing in action.

@@

\begin{figure}[!ht]
\includegraphics[width=0.8\textwidth]{figures/sit1-c0.pdf}
\caption{Sitting M=0}
\label{fig:sit1-c0}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=0.8\textwidth]{figures/sit1-c100.pdf}
\caption{Sitting M=100}
\label{fig:sit1-c100}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=0.8\textwidth]{figures/walk2-c0.pdf}
\caption{Walking M=0}
\label{fig:walk2-c0}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=0.8\textwidth]{figures/walk2-c100.pdf}
\caption{Walking M=100}
\label{fig:walk2-c100}
\end{figure}

>>>>

\usepackage{hyperref}

\begin{document}
\title{Body Area Network Platform Utilizing Energy-Efficient Routing of Physiological Data}
\author{Alvaro Prieto\\
Masters Thesis\\
BS/MS Electrical Engineering\\
Electrical and Microelectronic Engineering Department\\
Rochester Institute of Technology\\
Rochester, NY\\
\texttt{axp8664@rit.edu}}

\maketitle
\thispagestyle{empty}

@@

\addcontentsline{toc}{section}{\protect\numberline{}Table of Contents}
\tableofcontents

@@

\addcontentsline{toc}{section}{\protect\numberline{}List of Figures}
\listoffigures

@@

Finally, the program produced a graphical output. The graphical output began as a simple experiment to see a visual representation of the network. It was later expanded to generate graphs of the network, and all available connections, as the RSSI data was sampled. Due to the large number of links between all of the nodes, this graphic was not useful. The final implementation, which can be seen in Figure~\ref{fig:networkgraph1}, only displayed the links used in a specific round of routing. The link labels display the transmit power required by each node to meet the specific link. The generated graphs can later be put together to form an animation that shows the network changing in action. A sample video of the generated routing animation can be seen in \url{http://www.youtube.com/watch?v=5Mpn-_FFJaw&hd=1}.

@@

\begin{figure}[!htb]
\includegraphics[width=0.8\textwidth]{figures/sit1-c0.pdf}
\caption{Sitting M=0}
\label{fig:sit1-c0}
\end{figure}

\begin{figure}[!htb]
\includegraphics[width=0.8\textwidth]{figures/sit1-c100.pdf}
\caption{Sitting M=100}
\label{fig:sit1-c100}
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=0.8\textwidth]{figures/walk2-c0.pdf}
\caption{Walking M=0}
\label{fig:walk2-c0}
\end{figure}

\begin{figure}[!htb]
\includegraphics[width=0.8\textwidth]{figures/walk2-c100.pdf}
\caption{Walking M=100}
\label{fig:walk2-c100}
\end{figure}
